Cleaning the data

### 2017-12-07 Analysis/data_cleaning.Rmd
sorting testts

```{r}
# ## Disparity
# tests <- data[,8]

# unique(tests)

# ## ANOVA
# anova <- c("MANOVA", "PERMANOVA", "ANOVA")

# ## LDA
# LDA <- c("LDA")

# ## Model test
# models <- c("Model fitting")

# ## Mean test
# t_test <- c("t-test")

# ## Correlation
# correlation <- c("Correlation \\(Fisher's exact test \\+ Spearman's rank\\)")

# ## linear models
# linear <- c()

# NA 
# "MANOVA , LDA" 
# "PERMANOVA" 
# "Model fitting" 
# "t-test" 
# "ANOVA" 
# "Correlation (Fisher's exact test + Spearman's rank)"
# "Raup-space" 
# "?" 
# "PGLS (PC ~ trait)" 
# "Mantel test" 
# "Partial Least Squares" 
# "Morphological Disparity Index (MDI) statistics" 
# "Canonical analysis (PCM style)" 
# "NPMANOVA" 
# "Procrustes ANOVA" 
# "phyloANOVA" 
# "MANOVA" 
# "lm + t-test" 
# "Covariance ratio" 
# "PERMANOVA + CI overlap" 
# "Cluster dendrogram analysis" 
# "LDA" 
# "ANCOVA" 
# "phyloANOVA + phyloLDA" 
# "GLS" 
# "distance PGLS" 
# "neigbor joining of the centroids" 
# "comparison to a null expectancy" 
# "centre of gravity" 
# "multivariate regression" 
# "" 
# "linear regressions" 
# "confidence interval overlap" 
# "correlation tests" 
# "Mann-Whitney" 
# "Kruskal-Wallis test + Walsh F-test" 
# "Neares-neighbor test" 
# "Spearman correlation" 
# "coefficient of variance" 
# "GLS multiple regression" 
# "permutation test" 
# "Z-test" 
# "Anova + Kruskal-Wallis" 
# "Canonical variates analysis" 
# "F-statistics" 
# "Wilcoxon" 
# "multivariate t-test (Hotellings' T^2 test)" 
# "Nearest neigbhor clustering" 
# "Ripley's K" 
# "Hierarchical clustering" 
# "Canonical variance analysis" 
# "bootstrap/rarefaction null hypothesis" 
# "-" 
# "MANCOVA + MANOVA" 
# "Branching random walks" 
# "PICs" 
# "Kernel analysis" 
# "Multidimensional Convergence Index" 
# "Chi-squared" 
# "Multivariate PGLS" 
# "Kruskal-Wallis test" 
# "Breush-Pagan + disparity test" 
# "Non-linear regressions" 
# "regression score"

# test <- c("anova", "model fitting", "canonical", "confidence interval")
```

>>>>

```{r}
## Disparity
tests <- data[,8]

## ANOVA
anova <- c("MANOVA", "PERMANOVA", "ANOVA", "NPMANOVA", "Procrustes ANOVA", "phyloANOVA", "PERMANOVA", "ANCOVA", "phyloANOVA", "Kruskal-Wallis test", "coefficient of variance", "permutation test", "Anova", "Ripley's K", "MANCOVA", "Chi-squared")
tests <- multi.gsub(anova, "anova", tests)

## LDA
LDA <- c("LDA", "phyloLDA")
tests <- multi.gsub(LDA, "LDA", tests)

## Model test
models <- c("Model fitting", "comparison to a null expectancy", "bootstrap/rarefaction null hypothesis")
tests <- multi.gsub(models, "models", tests)

## Mean test
t_test <- c("t-test", "Mann-Whitney", "Walsh F-test", "Z-test", "F-statistics", "Wilcoxon", "multivariate t-test \\(Hotellings' T\\^2 test\\)")
tests <- multi.gsub(t_test, "t_test", tests)

## Correlation
correlation <- c("Correlation \\(Fisher's exact test \\+ Spearman's rank\\)", "Mantel test", "correlation tests", "Spearman correlation")
tests <- multi.gsub(correlation, "correlation", tests)

## regressions
linear <- c("PGLS \\(PC \\~ trait\\)", "Partial Least Squares", "Canonical analysis \\(PCM style\\)", "lm", "Covariance ratio", "GLS", "distance PGLS", "multivariate regression", "linear regressions", "GLS multiple regression", "PICs", "Multivariate PGLS", "Non-linear regressions", "regression score", "Breush-Pagan")
tests <- multi.gsub(linear, "linear", tests)

## non stat
non_stat <- c("CI overlap", "confidence interval overlap")
tests <- multi.gsub(non_stat, "non_stat", tests)

## other
other <- c("Morphological Disparity Index \\(MDI\\) statistics", "centre of gravity", "Canonical variates analysis", "Canonical variance analysis", "Multidimensional Convergence Index", "Kernel analysis", "disparity test")
tests <- multi.gsub(other, "other", tests)

## clustering
clustering <- c("Neares-neighbor test", "Cluster dendrogram analysis", "neigbor joining of the centroids", "Nearest neigbhor clustering", "Hierarchical clustering", "Branching random walks")
tests <- multi.gsub(clustering, "clustering", tests)

tests <- ifelse(tests == "", NA, tests)
tests <- ifelse(tests == "?", NA, tests)
tests <- ifelse(tests == "-", NA, tests)
tests <- ifelse(tests == "Raup-space", NA, tests)

## Clean the matchings
tests <- gsub("distance Plinear", "linear", tests)
tests <- gsub("multivariate t_test \\(Hotellings' T\\^2 test\\)", "t_test", tests)
tests <- gsub("anova , LDA", "anova + LDA", tests)
tests <- gsub("Kruskal-Wallis", "anova", tests)

tests_categories <- unique(unlist(strsplit(unique(tests), split = " \\+ ")))

data[,8] <- tests
```
